Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-30 ms.tex
intro

\section{Introduction} \label{sec:intro}
Planets are round, rotating, and irradiated on one hemisphere at a time -- all of which contribute to rich spatial structure in their climate and atmospheric composition.  Short period, tidally locked planets are an extreme example, with hot, continuously illuminated daysides. This asymmetry is expected to produce large gradients in temperature, chemistry, and cloud coverage with longitude \citep{showman09, kataria16, parmentier16}.

Extrasolar planets are so distant that they are not spatially resolved, so the only way to reveal this variation is to measure a phase curve. Phase curve observations consist of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet, which exposes different longitudes at each orbital phase.  The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep{parmentier17}.  \Kepler\ enabled the first measurements of phase curves at optical wavelengths \citep[e.g.]{esteves15}. \cite{stevenson14} observed the first \emph{spectroscopic} phase curve for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared. These observations had fairly good agreement with 3D GCM predictions, eastward-shifted peak brightness and more efficient heat redistribution for cooler planets. 
FIXME: say after Spitzer that results agree with GCM. Elaborate after esteves15 that the optical phase curves are sensitive to clouds.

>>>>

\section{Introduction} \label{sec:intro}
Planets are round, rotating, and irradiated on one hemisphere at a time -- all of which contribute to rich spatial structure in their climate and atmospheric composition.  Short period, tidally locked planets are an extreme example, with hot, continuously illuminated daysides. This asymmetry is expected to produce large gradients in temperature, chemistry, and cloud coverage with longitude \citep{showman09, kataria16, parmentier16}.  FIXME we want to understand this, heat circulation and atmospheric dynamics, and also to put transmission and emission spectra in context. Extrasolar planets are so distant that they are not spatially resolved, so the only way to reveal this variation is to measure a phase curve. Phase curve observations consist of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet, which exposes different longitudes at each orbital phase.

The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep{parmentier17}.  These observations revealed large day-night temperature contrasts (in excess of FIXME K), and eastward shifted peak brightness due to heat circulation.  These measurements were complemented by optical phase curves from \Kepler\, which are sensitive to reflected light \citep[e.g.]{esteves15}. FIXME clouds. \cite{stevenson14} observed the first \emph{spectroscopic} phase curve for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared. These observations had fairly good agreement with 3D GCM predictions, eastward-shifted peak brightness and more efficient heat redistribution for cooler planets.
